A thesis draft

### 2018-09-13 draft.tex
Add content about VIBES project

\author{Polonio Davide}
\title{A thesis draft}
% The outline'd be something like this:
%  Thesis outline
% 
% - Introduction about the VIBES project (context, 5G, the need for a new 
% network 
% architecture, proposed solution, requisites)
%   + Related works
% - Analysis of the available technologies (kubernetes, openstack, openvswitch, 
% docker, docker swarm)
%   + Choseen tecnhologies and description of the 'reason why'
% - Project description
%   + Initial solution with Openstack and Tacker
%   + From Tacker to Openbaton
%   + From Openbaton with Openstack to Openbaton with Docker
%   + Exploration of docker orchestrators (Swam vs Kubernetes)
%   + Kubernetes internal composition (GlusterFS, Ingress, Harbor, metrics)
%   + Openbaton and Kubernetes integration (lack of a implemented Driver, 
% integration with existinf VNFM)
% - Case study
%   + Analysis of TCP/UDP performance
% - Results
% - Future works
% - Conclusions

@@

 This thesis initially begun with the goals descripted in the VIBES\todo{Talk 
about VIBES project, add some reference, explain what it is.} project, where 
the necessity for better TCP/IP transmission through satellite connections was 
the main requirement. Starting with this objective, we encountered that, many 
networking tools already present in the market, required some tweaking and some 
integrations, shifting our goal to create a complete  ETSI (European
Telecommunications Standards Institutes) MANO testbed, following the 
specifications suggested in the RFC 7665.
\end{document}

>>>>

\author{Polonio Davide}
\title{A thesis draft}
% The outline'd be something like this:
%  Thesis outline
% 
% - Introduction about the VIBES project (context, 5G, the need for a new 
% network architecture, proposed solution, requisites)
%   + Related works
% - Analysis of the available technologies (kubernetes, openstack, openvswitch, 
% docker, docker swarm)
%   + Choseen tecnhologies and description of the 'reason why'
% - Project description
%   + Initial solution with Openstack and Tacker
%   + From Tacker to Openbaton
%   + From Openbaton with Openstack to Openbaton with Docker
%   + Exploration of docker orchestrators (Swam vs Kubernetes)
%   + Kubernetes internal composition (GlusterFS, Ingress, Harbor, metrics)
%   + Openbaton and Kubernetes integration (lack of a implemented Driver, 
% integration with existinf VNFM)
% - Case study
%   + Analysis of TCP/UDP performance
% - Results
% - Future works
% - Conclusions

@@

 This thesis is part of the VIBES project\todo{Talk about VIBES project, add 
some reference, explain what it is.}, where the necessity for better TCP/IP 
transmission through satellite connections is the main requirement. To 
reach this goal, the project specifications suggest to exploit the 5G incoming 
technology and use the NFV-MANO architecture to perform first packets 
elaboration and performance improvment and finally TCP/IP satellite chunk
optimization with the Performance Enhancing Proxy (PEP). The VIBES project 
proposed five technical requirements\todo{Finish list!}:
\begin{itemize}
 \item Analysis of the applicability of current and new Internet protocols in
the proposed VNF-PEP architecture
\end{itemize}

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools already 
present in the market required some tweaking and some integrations, shifting our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first three 
requisites, without digging in the satellite data flow optimization.
\end{document}
